---
title: "Market Basket Analysis"
author: "Jared"
date: "November 27, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Loading packages for association rules and the groceries dataset
library(arules)
library(arulesViz)
data("Groceries")
# The Groceries data set contains 1 month (30 days) of real-world point-of-sale transaction data
# from a typical local grocery outlet. The data set contains 9835 transactions and the items are 
# aggregated to 169 categories.


```

```{r}
summary(Groceries)

```



```{r}
rules <- apriori(Groceries,parameter = list(supp= .001, conf=.3, maxlen=5, target='rules'))

```


How many rules have a confidence of 1?

```{r}
subrules1 <-rules[quality(rules)$confidence == 1]
subrules1
```


```{r}
# Alternative approach
rules2 <- apriori(Groceries,parameter = list(supp= .001, conf=1, maxlen=5, target='rules'))
```


Which pairs have the highest lift?

```{r}
# Top 10 lift

inspect(head(sort(rules,by='lift'),10))

```


Which have the highest count?

```{r}
#Highest count
inspect(head(sort(rules,by='count'),10))


```


Which left hand side has highest lift when right hand side is only bottled beer?

```{r}
rule_bottledbeer <- apriori(Groceries,parameter=list(support =0.001, confidence =0.3, maxlen=5),
                       appearance = list(rhs=("bottled beer"), default="lhs"))
```

```{r}
inspect(head(sort(rule_bottledbeer,by='lift'),10))

```


Which right hand side has highest lift when left hand side is whole milk and any type of bread?

```{r}
breadItems <- grep("bread", itemLabels(Groceries), value = TRUE)
breadItems

```

```{r}
rules_bread_milk <- apriori(Groceries, 
                   parameter=list(support =0.001, confidence =0.3, maxlen=5), 
                   appearance = list(lhs=c("whole milk", breadItems), default="rhs"))

```

```{r}
inspect(head(sort(rules_bread_milk,by='lift'),10))

```

```{r}
inspect(head(sort(rules_bread_milk,by='count'),10))


```



Now we visualize our results, and we can even make an interactive plot to pick rules graphically and inspect them.

```{r}
plot(rules,engine="interactive")


```










